---
title: "R Notebook"
output: html_notebook
---

# Explore and Visualize (EDA)
## Plot 24 graphs (24 Facebook pages) :
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)

```

Note : set working directory before running this code below
```{r}

# All Facebook pages
pages = c('DramaAdd', 'ejeab', 'cartooneggcat', 'BBCThai', 'khobsanam', '1447102878929950',
          'powerofhusbands', 'basementkaraoke', 'cartoon5natee', 'AjahnBuddhadasa', 'Toodsdiary',
          'ceclip', 'beargirlfriend', 'jaytherabbitofficial', 'Darlingboredom', 'v.vajiramedhi', 
          '334236760084743', 'kingdomoftigers', 'underbedstar', 'pantipded', 'Pantip.KratooDed', 
          'nut.ped', '9gaginthai', 'in.one.zaroop')

indx = 1
graph.list = list() # list of ggplot results
allpages = data.frame()

# create graphs for each page :
for (page in pages){
  # cleaned ASCII characters in ID-MSG-LINK csv files by python, saved as *****IDnoASCII.csv, then run this :
  df = read.csv(paste0(page, 'IDnoASCII.csv'), fileEncoding = 'UTF-8-BOM', stringsAsFactors = F)
  tsdf = read.csv(paste0(page, '.csv'), fileEncoding = 'UTF-8-BOM', stringsAsFactors = F)
  
  # transform string to date format :
  df$created_time = as.POSIXct(df$created_time, format='%Y-%m-%dT%H:%M:%S%z')
  df$time_checked = as.POSIXct(df$time_checked, format = '%Y-%m-%d %H:%M:%S')
  tsdf$created_time = as.POSIXct(tsdf$created_time, format='%Y-%m-%dT%H:%M:%S%z')
  tsdf$time_checked = as.POSIXct(tsdf$time_checked, format = '%Y-%m-%d %H:%M:%S')
  
  # remove unwanted column, then unique by 'label1' column :
  df$message = NULL
  df = df %>% 
    distinct(label1, .keep_all = T)
  
  # remove minute and second of 'time_checked' column :
  df$time_checked = as.POSIXct(floor(as.numeric(df$time_checked)/(60*60))*(60*60), 
                               origin = '1970-01-01')
  tsdf$time_checked = as.POSIXct(floor(as.numeric(tsdf$time_checked)/(60*60))*(60*60), 
                                 origin = '1970-01-01')
  
  # add a new column which is the estimated value of 'reaction_count' after 1 hour of 'created_time' :
  hourcount = function(row){
    hour = 1*(60*60) ######### changeable 'hour'
    shifted.time = as.numeric(row$created_time) + hour
    hour.ratio = shifted.time / (60*60) - floor(shifted.time / (60*60))
    next.timestamp = ceiling(shifted.time / (60*60)) * (60*60)
    prev.timestamp = floor(shifted.time / (60*60)) * (60*60)
    next.count = tsdf[tsdf$time_checked == as.POSIXct(next.timestamp, origin = '1970-01-01') &
                        tsdf$label1 == row$label1, 'reaction_count'] ######## changeable 'count'
    prev.count = tsdf[tsdf$time_checked == as.POSIXct(prev.timestamp, origin = '1970-01-01') &
                        tsdf$label1 == row$label1, 'reaction_count'] ######## changeable 'count'
    if (length(next.count) == 0 | length(prev.count) == 0){
      return(NA)
    }
    else{
      count = prev.count + (hour.ratio * (next.count - prev.count))
      return(count)
    }
  }
  for (i in 1:nrow(df)){
    df[i, 'onehour_count'] = hourcount(df[i,])
  }
  
  # add 'time of the day' (tod) column :
  subdf = subset(df, created_time >= as.POSIXct('2016-11-16 10:05') & 
                   created_time <= as.POSIXct('2016-11-25 12:50'))
  subdf$created_tod = as.POSIXct(as.numeric(subdf$created_time) %% (60*60*24), origin = '2016-11-01')
  for (i in 1:nrow(subdf)){
    if (subdf$created_tod[i] > as.POSIXct('2016-11-01 23:59:50')){
      subdf$created_tod[i] = subdf$created_tod[i] - (24*60*60)
    }
  }
  
  # add 'days of the week' (dow) column :
  subdf$created_dow = as.POSIXlt(subdf$created_time)
  subdf$created_dow = subdf$created_dow$wday
  subdf$created_dow = ifelse(subdf$created_dow == 0, 'Sun', subdf$created_dow)
  subdf$created_dow = ifelse(subdf$created_dow == 1, 'Mon', subdf$created_dow)
  subdf$created_dow = ifelse(subdf$created_dow == 2, 'Tue', subdf$created_dow)
  subdf$created_dow = ifelse(subdf$created_dow == 3, 'Wed', subdf$created_dow)
  subdf$created_dow = ifelse(subdf$created_dow == 4, 'Thu', subdf$created_dow)
  subdf$created_dow = ifelse(subdf$created_dow == 5, 'Fri', subdf$created_dow)
  subdf$created_dow = ifelse(subdf$created_dow == 6, 'Sat', subdf$created_dow)
  # Group: Mon-to-Fri and Sat-to-Sun
  subdf$created_dow_cat = ifelse(subdf$created_dow %in% c('Sat', 'Sun') , 'S-S', 'M-F')
  
  
  # All pages rbind to one dataframe
  allpages = bind_rows(allpages, subdf)
  
  
  # Plots
  graph = ggplot(data = subdf, aes(x= created_tod, y=onehour_count)) +
    geom_point(aes(color = created_dow_cat), size = 2) +
    scale_x_datetime(date_labels = '%H:%M', date_breaks = 'hour',
                     limits = c(as.POSIXct('2016-11-01'), as.POSIXct('2016-11-02'))) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.3)) +
    labs(title = paste0('Page ID : ',page), subtitle = '1 Point = 1 Post', 
         x = "Created time of the day", y = "Reaction count after 1 hour of created time",
         color = 'Days of the week') +
    scale_color_hue(labels = c('Mon-Fri', 'Sat-Sun'))
  
  # save to list :
  graph.list[[indx]] = graph
  indx = indx + 1
}


```

Print in markdown :
```{r}

for(i in 1:length(graph.list)){
  print(graph.list[[i]])
}

```

Write all plots into a pdf file:
```{r}

pdf(file = 'Plots_24pages.pdf', width = 16, height = 9, onefile = T)
i = 1
while(i <= length(graph.list)){
  print(grid.arrange(grobs = graph.list[i:(i+5)], nrow = 3, ncol = 2))
  i = i + 6
}
dev.off()

```

## Combine all plots into one graph :
I use a linear transformation to transform each graph's mean and sd to 0.5 and 0.1 respectively.
Note that this is not a good analysis method at all, I'm just curious and want to practice my coding skill.
```{r}
allpages2 = allpages
# There are identical page names, so I have to seperate them before doing linear transformation :
allpages2[grep('543209025719472', allpages2$id, value = F), 'from'] = 'กระทู้เด็ด Pantip'
  allpages2 = allpages2 %>%
  subset(!is.na(onehour_count)) %>% 
  group_by(from) %>% 
  mutate(onehour_zscore = (onehour_count - mean(onehour_count)) / sd(onehour_count)) %>% 
  ungroup()
allpages2$onehour_norm = 0.5 + (0.1 * allpages2$onehour_zscore)

```

Plot:
```{r}
graph2 = ggplot(data = allpages2, aes(x= created_tod, y=onehour_norm)) +
    geom_point(aes(color = created_dow_cat), size = 2) +
    geom_hline(yintercept = 0.5, linetype = 2) +
    scale_x_datetime(date_labels = '%H:%M', date_breaks = 'hour',
                     limits = c(as.POSIXct('2016-11-01'), as.POSIXct('2016-11-02'))) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.3)) +
    labs(title = 'All pages in one plot', subtitle = '1 Point = 1 Post, Mean = 0.5, SD = 0.1', 
         x = "Created time of the day", y = "Reaction count after 1 hour of created time",
         color = 'Days of the week') +
    scale_color_hue(labels = c('Mon-Fri', 'Sat-Sun'))
print(graph2)

```

To PDF:
```{r}
pdf(file = 'Plot_AllinOne.pdf', width = 16, height = 9, onefile = T)
print(graph2)
dev.off()

```



